### 2018-02-21 latex/egsr17-cgf/introduction.tex
started working on anisotropy test case

Simulating light transport in paticipating media is still a challenging problem for image synthesis in computer graphics. Monte Carlo based techniques have established as the standard approach, because they can produce unbiased results and are conceptionally easy to implement. They become computationally demanding however, for participating media, which exhibits strong scattering or anisotropy.

>>>>

Simulating light transport in paticipating media is still a challenging problem for image synthesis in computer graphics. Monte Carlo based techniques are established as the standard approach, because they can produce unbiased results and are conceptionally easy to implement. They become computationally demanding however, for participating media, which exhibits strong scattering or anisotropy.

### 2018-02-21 latex/egsr17-cgf/main-body.tex
started working on anisotropy test case

@@

%-------------------------------------------------------------------------
\begin{document}
% uncomment for using teaser
\teaser
{
\centering
\begin{subfigure}{0.2\linewidth}
\missingfigure{}
\vspace{-0.17in}
\caption{Classical diffusion}
\end{subfigure}%
\hspace{0.05\linewidth}
\begin{subfigure}{0.2\linewidth}
\missingfigure{}
\vspace{-0.17in}
\caption{Flux-limited diffusion}
\end{subfigure}%
\hspace{0.05\linewidth}
\begin{subfigure}{0.2\linewidth}
\missingfigure{}
\vspace{-0.17in}
\caption{ours}
\label{fig:nebulae_ours}
\end{subfigure}%
\hspace{0.05\linewidth}
\begin{subfigure}{0.2\linewidth}
\missingfigure{}
\vspace{-0.17in}
\caption{Ground truth}
\end{subfigure}%
%\includegraphics[width=\linewidth]{figures/eg_new}
\vspace{-0.1in}
\icaption
{
Flux-limited diffusion (b) is an ad-hoc extension to the classical diffusion approximation (a). It can be considered the state of the art among deterministic methods for simulating light transport in highly scattering participating media, which is a common challenge for brute-force path tracing (d). We add the $P_N$-method (c) to the toolbox of deterministic methods in rendering and investigate its benefits and tradeoffs against flux-limited diffusion.
}
\label{fig:teaser}
}

>>>>

\author
{
Compiled on \today
%David Koerner$^{1,2,3}$
%\qquad Jan Nov\'ak$^{1}$
%\qquad Peter Kutz$^{2}$
%\qquad Ralf Habel$^{2}$
%\qquad Wojciech Jarosz$^{1,4}$
\\
% For Computer Graphics Forum: Please use the abbreviation of your first name.
%$^1$Disney Research
%\qquad $^2$Walt Disney Animation Studios
%\qquad $^3$University of Stuttgart
%\qquad $^4$Dartmouth College
}

@@

%-------------------------------------------------------------------------
\begin{document}
% uncomment for using teaser
\teaser
{
\centering
\begin{subfigure}{0.24\linewidth}
%\missingfigure{}
\includegraphics[width=\linewidth]{images/nebulae_ms_cda.png}
\vspace{-0.17in}
\caption{Classical diffusion}
\label{fig:teaser_cda}
\end{subfigure}%
\hspace{0.002\linewidth}
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{images/nebulae_ms_p5.png}
\vspace{-0.17in}
\caption{$P_5$ (ours)}
\label{fig:nebulae_ours}
\label{fig:teaser_pn}
\end{subfigure}%
\hspace{0.002\linewidth}
\begin{subfigure}{0.24\linewidth}
%\missingfigure{}
\includegraphics[width=\linewidth]{images/nebulae_ms_fld.png}
\vspace{-0.17in}
\caption{Flux-limited diffusion}
\label{fig:teaser_fld}
\end{subfigure}%
\hspace{0.002\linewidth}
\begin{subfigure}{0.24\linewidth}
%\missingfigure{}
\includegraphics[width=\linewidth]{images/nebulae_ms_groundtruth.png}
\vspace{-0.17in}
\caption{Ground truth}
\label{fig:teaser_gt}
\end{subfigure}%
%\includegraphics[width=\linewidth]{figures/eg_new}
\vspace{-0.1in}
\icaption
{
Flux-limited diffusion (\subref{fig:teaser_fld}) is an ad-hoc extension to the classical diffusion approximation (\subref{fig:teaser_cda}). It can be considered the state of the art among deterministic methods for simulating light transport in highly scattering participating media, which is a common challenge for brute-force path tracing (\subref{fig:teaser_gt}). We add the $P_N$-method (\subref{fig:teaser_pn}) to the toolbox of deterministic methods in rendering and investigate its benefits and tradeoffs against flux-limited diffusion.
}
\label{fig:teaser}
}

### 2018-02-21 latex/egsr17-cgf/previous_work.tex
started working on anisotropy test case

The $P_N$-method has a long history in other fields and was never applied in graphics. Kajia~\cite{Kajiya84} explained the theory, but did not give any details on implementation or how to solve it. In fact, as Max~\cite{Max95} pointed out, it is not clear if Kajiya succeeded at all at applying the method, as all of the results in the paper were produced with a simpler method. This is further strengthened by our observation, that a straight forward finite difference discretization of the $P_N$-equations produces unuseable results, due to oscillation artifacts in the solution. In our paper, we derive the real-valued $P_N$-equations along with a staggered-grid solver, that produces artifact free solutions.

>>>>

The $P_N$-method has a long history in other fields and was never applied in graphics. Kajia~\cite{Kajiya84} explained the theory, but did not give any details on implementation or how to solve it. In fact, as Max~\cite{Max95} pointed out, it is not clear if Kajiya succeeded at all at applying the method, as all of the results in his paper were produced with a simpler method. This is further strengthened by our observation, that a straight forward finite difference discretization of the $P_N$-equations produces unuseable results, due to oscillation artifacts in the solution. In our paper, we derive the real-valued $P_N$-equations along with a staggered-grid solver, that produces artifact free solutions.

### 2018-02-21 latex/egsr17-cgf/solver.tex
started working on anisotropy test case

Finally, the generated linear system is solved using standard methods. The solution $\vec{u}$ represents the discretized radiance field $\widehat{L}$, which is evaluated using using trilinear interpolation of the SH coefficients. An overview of the solver is given in figure~\ref{fig:pnsolver}. Each step will be described in more detail in the following subsections.

@@

Our computer algebra representation is based on mathematical expression trees, hierarchies composed out of expression instances. Those can be basic primitives, such as numbers, variables or special symbols, such as the Kronecker delta or imaginary number. Other expression types, such as integrals, derivatives, sums, products and functions build the hierarchy by referencing child expressions.

@@

The $P_N$-equations have been discretized, and the stencil has been generated, without any notion of domain boundaries and boundary conditions (BC). Our solver supports Neumann BC and Dirichlet BC. They are handled transparently by the code which runs the stencil. Whenever the stencil writes into $A$ for a boundary coefficient, the framework will either ignore the write operation (Dirichlet BC) or return the row and column in $A$ for the same coefficient of the closest voxel inside the domain (Neumann BC).

@@

\begin{figure}[h]
\centering
\begin{subfigure}{0.45\columnwidth}
\missingfigure{test}
\end{subfigure}%
\hspace{0.05\columnwidth}
\begin{subfigure}{0.45\columnwidth}
\missingfigure{test2}
\end{subfigure}%
\vspace{-0.2in}
\icaption{The solution of our solver for the 2D-checkerboard problem with collocated grids (left), where all coefficients are located at the cell centers. It suffers from severe oscillating artefacts, which are removed by offseting the coefficient locations using staggered grids (right).}
\label{fig:artefacts}
\end{figure}

>>>>

Finally, the generated linear system is solved using standard methods. The solution $\vec{u}$ represents the discretized radiance field $\widehat{L}$, which is evaluated using trilinear interpolation of the SH coefficients. An overview of the solver is given in figure~\ref{fig:pnsolver}. Each step will be described in more detail in the following subsections.

@@

Our computer algebra representation is based on mathematical expression trees, which are hierarchies of expression instances. Those can be basic primitives, such as numbers, variables or special symbols, such as the Kronecker delta or imaginary number. Other expression types, such as integrals, derivatives, sums, products and functions build the hierarchy by referencing child expressions.

@@

The $P_N$-equations have been discretized, and the stencil has been generated, without any notion of domain boundaries and boundary conditions (BC). Our solver supports Neumann BC and Dirichlet BC. They are handled transparently by the code which runs the stencil. Whenever the stencil writes into $A$ for a boundary coefficient, the framework will either ignore the write operation (Dirichlet BC) or write into the row and column in $A$ of the same coefficient at the closest voxel inside the domain (Neumann BC).

@@

\begin{figure}[h]
\centering
\begin{subfigure}{0.45\columnwidth}
%\missingfigure{test}
\includegraphics[width=\columnwidth]{images/checkerboard2d_p1_collocated.png}
\end{subfigure}%
\hspace{0.05\columnwidth}
\begin{subfigure}{0.45\columnwidth}
%\missingfigure{test2}
\includegraphics[width=\columnwidth]{images/checkerboard2d_p1_staggered.png}
\end{subfigure}%
\vspace{-0.1in}
\icaption{The solution of our solver for the 2D-checkerboard problem with collocated grids (left), where all coefficients are located at the cell centers. It suffers from severe oscillating artifacts, which are removed by offsetting the coefficient locations using staggered grids (right).}
\label{fig:artifacts}
\end{figure}
